---
title: "Prediction-CV1"
author: "Ye Bi"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/Library/CloudStorage/OneDrive-VirginiaTech/Research/Codes/research/BCS/BodyWeight/Github")
```

## Loading packages 
```{r}
library(readxl)
library(tidyverse)
library(reshape2)
library(MLmetrics)
library(caret)
library(RColorBrewer)
library(Metrics)
library(lme4)
```

## Load all self-made functions.
```{r}
source("./Functions.R")
```


## Build CV split in caret.
- Ref: https://topepo.github.io/caret/index.html
- Caret combines lots of functions, we can run basic machine learning models with hyperparameter tunning in it.
```{r}
train_control = trainControl(method="cv", number = 5, savePredictions = TRUE, classProbs = F)
train_control0 = trainControl(method="none", savePredictions = TRUE, classProbs = F)
```

## CV1: Forcasting CV 
- Building function
- 90:10
- 80:20
- 70:30
- 60:40
- 50:50
### Build function for cv1

```{r}
cv1_func <- function(data.df, ntrn, pred_method){
            # ntrn = 25
            train.df = data.df %>% filter(day <= ntrn) %>% droplevels()
            test.df = data.df %>% filter(day > ntrn) %>% droplevels()
            
            data.df.scale = cbind.data.frame(data.df[,-c(6,7,8,9,10)], scale(data.df[,c(6,7,8,9,10)], center = T, scale = T))
            train.df.scale = data.df.scale %>% filter(day <= ntrn) %>% droplevels()
            test.df.scale = data.df.scale %>% filter(day > ntrn) %>% droplevels()
            
                         if(pred_method == "RF"){
                                fit <- caret::train(BW~. ,
                                                   data=train.df[,c(2,6,7,9,10)],
                                                   method="rf",
                                                   trControl=train_control0,
                                                   tuneGrid = expand.grid(mtry=4))}
                                
                          
                          if(pred_method == "OLS"){
                                formu = paste("BW~1+", paste(colnames(train.df)[c(6,7,9,10)], collapse = "+"), sep = "")
                                fit <- lm(formu, data = train.df)}
                          
    
                          
                          if(pred_method == "L1"){
                             fit = caret::train(BW~. ,
                                                data=train.df[,c(2,6,7,9,10)], 
                                                method="glmnet", 
                                                trControl=train_control0,
                                                verbose = FALSE)
                                                tuneGrid = expand.grid(alpha = 1,
                                                                       lambda = 30)                          
                          }
                          
                          
                          if(pred_method == "L2"){
                             fit = caret::train(BW~. ,
                                                data=train.df[,c(2,6,7,9,10)], 
                                                method="glmnet", 
                                                trControl=train_control0,
                                                verbose = FALSE,
                                                tuneGrid = expand.grid(alpha = 0,
                                                                       lambda = 30))                         
                          }
                          
                          if(pred_method == "LMM"){
                            fit = lmer(BW ~ 1 + Width + Length + Height_average + Volume + (1+day_time_num|ID), 
                                       data=train.df.scale, 
                                       REML=F, 
                                       control = lmerControl(optimizer ="Nelder_Mead"))
                            test.df = test.df.scale
                          }
            
                            ## Metrics #####################
                            pred = predict(fit, test.df)
                            r2 = cor(pred, test.df$BW, use="complete.obs")^2
                            # rmse = mean((pred - test.df$BW)^2, na.rm = T)^0.5
                            rmse = Metrics::rmse(test.df$BW, pred)
                            mape = MLmetrics::MAPE(pred, test.df$BW)*100
                            
                            ##
                            pred.vector = c(r2, rmse, mape)
                            names(pred.vector) = c("R2", "RMSE", "MAPE")

            return(pred.vector)
}
```

### Fucntion to use CV1 and return pred results.
```{r}
Fitting_cv1_func = function(img_method, pred_method){
            #loading list data
                  data.df = preprosess_func(img_method)
            #fitting cv1      
                  predr.mat = matrix(NA, nrow = 5, ncol = 3);rownames(predr.mat) = c("cv90", "cv80", "cv70", "cv60", "cv50"); colnames(predr.mat) = c("R2", "RMSE", "MAPE")
                  predr.mat[1,] = cv1_func(data.df, ntrn = round(28*0.9), pred_method = pred_method)
                  predr.mat[2,] = cv1_func(data.df, ntrn = round(28*0.8), pred_method = pred_method)
                  predr.mat[3,] = cv1_func(data.df, ntrn = round(28*0.7), pred_method = pred_method)
                  predr.mat[4,] = cv1_func(data.df, ntrn = round(28*0.6), pred_method = pred_method)
                  predr.mat[5,] = cv1_func(data.df, ntrn = round(28*0.5), pred_method = pred_method)
                  print(round(predr.mat, 2)[,c(1,2,3)])
                  return(round(predr.mat, 2)[,c(1,2,3)])
                  cat("\n \n")
          }
```

```{r}
l11 = Fitting_cv1_func("ST", "OLS")
l12 = Fitting_cv1_func("AT", "OLS")
l13 = Fitting_cv1_func("MRCNN", "OLS")


# Fitting_cv1_func("ST", "RF")
# Fitting_cv1_func("AT", "RF")
# Fitting_cv1_func("MRCNN", "RF")

l21 = Fitting_cv1_func("ST", "L2")
l22 = Fitting_cv1_func("AT", "L2")
l23 = Fitting_cv1_func("MRCNN", "L2")

l31 = Fitting_cv1_func("ST", "L1")
l32 = Fitting_cv1_func("AT", "L1")
l33 = Fitting_cv1_func("MRCNN", "L1")

l41 = Fitting_cv1_func("ST", "LMM")
l42 = Fitting_cv1_func("AT", "LMM")
l43 = Fitting_cv1_func("MRCNN", "LMM")
```

```{r}
temp = rbind(cbind(l11[,1],l21[,1],l31[,1],l41[,1],l11[,3],l21[,3],l31[,3],l41[,3]),
      cbind(l12[,1],l22[,1],l32[,1],l42[,1],l12[,3],l22[,3],l32[,3],l42[,3]),
      cbind(l13[,1],l23[,1],l33[,1],l42[,1],l13[,3],l23[,3],l33[,3],l43[,3]))
rownames(temp) = rep(c("90:10", "80:20", "70:30", "60:40", "50:50"), 3)
temp0 = temp
for(i in 1:15){
  for(j in 1:8){
    temp0[i, j] = paste0("&", temp[i,j])
  }
}
print(temp0)
```



## Linear mixed model
```{r}
lmm.func = function(img_method){
          
          data.df = preprosess_func(img_method)
          #sample code  
          data.df.scale = cbind.data.frame(data.df[,-c(6,7,8,9,10)], scale(data.df[,c(6,7,8,9,10)], center = T, scale = T))
          train.df = data.df.scale
          test.df = data.df.scale
          m <- lmer(BW ~ 1 + Width + Length + Height_average + Volume + (1+day_time_num|ID), data=data.df.scale, REML=F, control = lmerControl(optimizer ="Nelder_Mead"))
          fit = m
          pred = predict(fit, test.df)
          r2 = cor(pred, test.df$BW, use="complete.obs")^2
          # rmse = mean((pred - test.df$BW)^2, na.rm = T)^0.5
          rmse = Metrics::rmse(test.df$BW, pred)
          mape = MLmetrics::MAPE(pred, test.df$BW)*100
          AIC = AIC(fit)
          BIC = BIC(fit)
          
          ##
          pred.vector = c(r2, rmse, mape, AIC, BIC)
          names(pred.vector) = c("R2", "RMSE", "MAPE", "AIC", "BIC")
          cat("goodness of fit: \n")
          print(round(pred.vector, 2))
          cat("\n")
          
          int = sum(summary(m)$coefficients[,1])
          ranef1 = ranef(m)$ID
          lmm.df = cbind.data.frame(ID = 1:12, slope = ranef1$day_time_num, intercept = int + ranef1$`(Intercept)`)
          lmm.df$ID = factor(lmm.df$ID, levels = 1:12)
          p=ggplot(data.df,aes(x=day_time_num,y=BW,color=ID))+
            geom_abline(data = lmm.df, aes(slope=slope, intercept = intercept, color = ID))+
            geom_point()+
            # facet_wrap(~ID,nrow=3)+
            theme_classic()+
            ggtitle(img_method)+
            theme(plot.title = element_text(size=25, face = "bold", hjust = 0), 
                  axis.title.x = element_text(size = 16),
                  axis.title.y = element_text(size = 16),
                  axis.text.x = element_text(size = 11, angle = 90,hjust=1,vjust=0.5), 
                  axis.text.y = element_text(size = 11, vjust=0.5))
          return(p)
          }
```


```{r}
p1 = lmm.func("ST")
p2 = lmm.func("AT")
p3 = lmm.func("MRCNN")
ggpubr::ggarrange(p1, p2, p3,
                  ncol = 2, nrow = 2)
# dev.print(pdf, file="./outputs/lmm.pdf", height = 11, width = 11)
```
## Done with preprocessing for preprosess_func 
goodness of fit: 
     R2    RMSE    MAPE     AIC     BIC 
   0.98   19.07    1.80 4311.78 4349.29 

## Done with preprocessing for preprosess_func 
goodness of fit: 
     R2    RMSE    MAPE     AIC     BIC 
   0.98   19.11    1.80 4013.15 4049.99 

## Done with preprocessing for preprosess_func 
goodness of fit: 
     R2    RMSE    MAPE     AIC     BIC 
   0.98   19.66    1.82 4423.95 4461.65 
   

